%----------------------------------------------------------------------
% @brief    LaTeX2e Resume for Chirag Kantharia
\documentclass[margin,line]{resume}

%----------------------------------------------------------------------
\begin{document}
\name{\Large Chirag Kantharia}
\begin{resume}

    %__________________________________________________________________
    % Summary 
    \section{\mysidestyle Summary}

    Hands-on software architect/tech lead with over 15 years experience
    in systems programming on Linux and FreeBSD. Expertise programming
    with C, C++, Shell, Perl and Python in UNIX environment. In my spare
    time, I like to read and write suckless software.

    %__________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Juniper Networks}, Bangalore, India \\\vspace{1mm}%
    \textsc{Staff Engineer} \hfill \textbf{Nov 2004 -- present}\\
    Currently designing a {\bf cross platform SDK} for data center
    customers to enable high IQ applications on Juniper switches.
    Designed and developed the {\bf control plane software},
    comprising of chassis management, line-card discovery, power
    management and software upgrade process, for several Juniper
    platforms including {\bf M-series}, {\bf MX-series}, {\bf
    T-series} routers, and {\bf CSE2000}. Delivered infrastructure for
    {\bf In-Service Software Upgrade} with minimal traffic disruption
    for single-chassis and multi-chassis Juniper routers. Wrote
    diagnostics software for {\bf Intel 1GbE NIC}. Wrote scripts to
    monitor the sizes of prime data structures across releases in
    JUNOS to help monitor the scaling limits. Board bringup of JUNOS
    on {\bf M120}, {\bf MX960} routers and {\bf T4000} line card.
    Presented tech talks to developer community, reviewed several
    thousand lines of code.

    \textbf{Hewlett-Packard}, Bangalore, India \\\vspace{1mm}%
    \textsc{Senior Software Engineer} \hfill \textbf{Jun 2003 -- Oct 2004}\\
    Release manager for {\bf Linux} device drivers for {\bf Compaq
    CISS} and {\bf Compaq CPQARRAY} hardware RAID cards for multiple
    Linux distributions including {\bf RedHat}. {\bf SUSE}, and {\bf
    Debian}, across multiple architectures. Responsible for parallel
    cluster boot and process monitoring on {\bf OpenSSI}. Assisted
    beta customers to help scale vendor applications on {\bf OpenSSI}.
    Trained and mentored developers.

    \textbf{Timesys Inc}, Bangalore, India \\\vspace{1mm}%
    \textsc{Linux Kernel Engineer} \hfill \textbf{Mar 2002 -- Apr 2003}\\
    Responsible for Timesys BSP on Embedded Planet SBC, IBM Walnut
    PowerPC SBC and on Applied Data Systems Graphics Client Plus SBC.
    Helped develop build infrastructure for Timesys Linux distribution
    bundled with Eclipse based IDE.

    \textbf{Epigon Audiocare Pvt Ltd}, Bangalore, India \\\vspace{1mm}%
    \textsc{Software Engineer} \hfill \textbf{Dec 2000 -- Feb 2002}\\
    Responsible for {\bf Linux 2.4} \& {\bf Linux 2.2} device driver
    for {\bf C-sound PCI music synthesis card}. Developed clean-room
    implementation of {\bf Java Virtual Machine} conforming to subset
    of {\bf J2ME} specification.
    

    %__________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming} 

    C, Python, Perl, BASH, CVS, SVN, GIT, Apache HTTPD, Gnats,
    RedMine, multithreading/multiprocessing, async/event-driven
    programming, distributed/grid computing, large scale software
    design, test-driven development.

    %__________________________________________________________________
    % Personal
    %\section{\mysidestyle Personal} 
    %{\sl US/UK dual citizen, able to work without restrictions in the US and European Union}

    %__________________________________________________________________
    % Education
    \section{\mysidestyle Education}
	\textbf{Indian Institute of Technology}, Mumbai, India. \hfill \textbf{1995--2000}\\
	\textsc{B.Tech Computer Science and Engineering} \\

    %------------------------------------------------------------------
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    201, Rahat Residency,  \hfill chyrag@yahoo.com \\
    Nagavarapalya-Varthur Road, C.V.Ramanagar, \hfill kantharia.in/chirag \\
    Bangalore, India  \hfill linkedin.com/pub/chirag-kantharia/1/160/371 \\
    mobile: +91 98455 68691  \hfill github.com/chyrag \\

%______________________________________________________________________
\end{resume}
\end{document}

% EOF

