\documentclass[12pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[scale=0.80]{geometry}

\name{Chirag}{Kantharia}
\address{201, Rahat Residency, Nagavarapalya-Varthur Road, C V Ramanagar, Bangalore, INDIA}
\phone{+91.98455.68691}
\email{chirag.kantharia@gmail.com}
% \extrainfo{* 01 December 1976}

\begin{document}
\makecvtitle

\section{Summary}
\cvlistitem{Experienced system software developer on Linux and FreeBSD,
  passionate about building networking products that sustain test of time, with
  proclivity for minimalism, beautiful code and elegant architecture.
  Identifying bottlenecks, building productivity tools, automating work flows
  are my areas of interest.}

\section{Skills}
\cvlistitem{Software Architecture, Virtualization, Networking}
\cvlistitem{System Programming (Linux, FreeBSD)}
\cvlistitem{C, C++, Python, Perl, BASH, make, GDB, gprof, perf, Git, SVN, CVS}

\section{Education}
\cventry{1995--2000}{B.Tech}{Indian Institute of Technology, Bombay}
        {Powai}{Mumbai} {Computer Science and Engineering}

\section{Work Experience}

\cventry{Jan 2015 - present}{Software Engineer}{Versa Networks Inc}{Bangalore}{India}{}{}

\cvlistitem{I develop and maintain publisher-subscriber model based
  infrastructure for control plane and data plane redundancy for an SDN
  controller.}

\cvlistitem{I built a tool to monitor the IPC messages sent from various
  components to other components, enabling message tracing and trouble
  shooting.}

\vspace{10px}
\cventry{Nov 2004 - Dec 2014}{Staff Engineer}{Juniper Networks Inc}{Bangalore}{India}{}{}

\cvlistitem{I developed publisher-subscriber based server backend for a product
  offering API for programmable networks, to push actionable network events to
  subscribers.}

\cvlistitem{I delivered hardened, high-performance service provider appliance,
  CSE2000, that acted as an external service card on PTX5000, which delivered
  wide range of controller, scaling and network function virtualization (NFV)
  applications. My responsibility was the control plane software including
  chassis management which comprised of reading sensor data off I2C devices,
  managing alarm conditions, handling IPMI events, pushing interface events to
  the main control board running JUNOS.}

\cvlistitem{I developed control plane software for T4000 line card, including
  board initialization, communciation with the control board running JUNOS, and
  driver for FPGA which enabled remote upgrade.}

\cvlistitem{I developed infrastructure for in-service software upgrade for
  Juniper T-series and M-series routers. My responsibility comprised of the
  in-service upgrade control flow, and replication of kernel state across
  heterogenous kernel versions. The feature enables Juniper routers to carry out
  software upgrade in production environment with minimal or zero traffic loss.}

\cvlistitem{I developed infrastructure for high availability and redundancy for
  control plane, known as GRES (Graceful RE Switchover), which comprised of
  replicating kernel state and maintaining backup of the hard disk data, on a
  standby node for Juniper routers with dual routing engines.}

\cvlistitem{I developed tools for monitoring scaling numbers for Juniper routers
  across releases. This helps the competitive edge team to ensure that Juniper
  routers scaled to the published numbers.}

\cvlistitem{I created a HAL abstraction layer making it easier to port JUNOS to
  new platforms. I developed diagnostic software to validate new hardware on the
  new platforms.}

\cvlistitem{Feature enhancement and sustenance of JUNOS kernel.}

\vspace{10px}
\cventry{Jun 2003 - Oct 2004}{Senior Software Engineer}{Hewlett-Packard}{Bangalore}{India}{}{}

\cvlistitem{I developed parallel boot mechanism for OpenSSI, Linux cluster
  project sponsored by HP. I was also official release engineer for the project
  for several releases. I also helped beta customers to scale their application
  on the cluster.}

\cvlistitem{I maintained CPQARRAY, CPQFC device drivers in the mainline Linux
  kernel, and support for the drivers in HP volume manager utility. I created
  the distribution packages for various mainstream Linux distributions including
  RedHat and SUSE.}

\vspace{10px}
\cventry{Mar 2002 - Apr 2003}{Software Engineer}{Timesys Inc}{Bangalore}{India}{}{}

\cvlistitem{I ported Timesys Linux to various PowerPC and StrongARM based single
  board computers, which comprised of getting the Timesys Linux to boot up on
  the board and getting the serial console and ethernet working.}

\cvlistitem{I setup up build server which built shippable CD images to customers.}

\vspace{10px}
\cventry{Dec 1999 - Feb 2002}{Software Engineer}{Epigon Audiocare}{Bangalore}{India}{}{}

\cvlistitem{I developed a clean-room implementation of Java Virtual Machine
  adhering to J2ME/MIDP specifications intended to run on a Linux 2.2 based
  embedded system.}

\cvlistitem{Developed Linux 2.4 device driver for in-house developed PCI card
  for C-sound music synthesis.}

\end{document}
