\documentclass[11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{hyperref}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

% Make lists without bullets and compact spacing
% \renewenvironment{itemize}{
% 	\begin{list}{}{
% 		\setlength{\leftmargin}{1.5em}
% 		\setlength{\itemsep}{0.25em}
% 		\setlength{\parskip}{0pt}
% 		\setlength{\parsep}{0.25em}
% 	}
% }{
% 	\end{list}
% }


%-------------------------------------------------------------------------------
%Custom commands
\newcommand{\resitem}[2]{\item \textbf{#1:} #2}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
% \newcommand{\ressubheading}[4]{
% 	\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
% 	\textbf{#1} & \textsc{#2} \\
% #3 & #4 \\
% 	\end{tabular*}}
\newcommand{\ressubheading}[3]{\item \textbf{#1} (\textsc{#2}, #3) }
%-------------------------------------------------------------------------------
% Variables
\def\footerlink{http://kantharia.in/chirag/resume/}

%-------------------------------------------------------------------------------

\begin{document}

%-------------------------------------------------------------------------------
%-- Heading --------------------------------------------------------------------
%-------------------------------------------------------------------------------

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Chirag Kantharia}		  & chirag@kantharia.in \\
201, Rahat Residency, Nagavarapalya-Varthur Road  & http://kantharia.in/chirag/ \\
C.V.Ramanagar 		  & +91.80.4160.5506 \\
Bangalore, India 560093 			  & \\
\end{tabular*}

%-------------------------------------------------------------------------------
%-- Summary --------------------------------------------------------------------
%-------------------------------------------------------------------------------
\vspace{0.1in}
\resheading{Summary}
\begin{itemize}

\item Over 12 years of industry experience of system programming in FreeBSD \& Linux.
\item Strong system view, good design skills with exposure to embedded systems, high end routers, and virtual machines.
\item Managed small teams and led projects to successful completion.
\item Fast learner, with wide range of practical skills.

\end{itemize}

%-------------------------------------------------------------------------------
%-- Skills ---------------------------------------------------------------------
%-------------------------------------------------------------------------------
\vspace{0.1in}
\resheading{Skills}

\begin{itemize}
\item Programming experience in C (expert), Bash shell (expert), Perl (expert) in UNIX environment.
\item Development tools: Make, CVS, Subversion.
\item Operating systems: FreeBSD, Linux (Debian, Redhat)
\end{itemize}

%-------------------------------------------------------------------------------
%-- Work Experience ------------------------------------------------------------
%-------------------------------------------------------------------------------
\vspace{0.1in}
\resheading{Work Experience}
\begin{itemize}
  \ressubheading{Juniper Networks India}{Staff Engineer}{Nov 2004 - Present}
    \begin{itemize}

    \resitem{Platform software}{I am part of the team that develops support for
    new Juniper platforms for Core Business Unit. I work closely with the
    hardware team for the control plane bringup, developing FreeBSD based
    software called JUNOS that runs on control boards managing the chassis, and
    the home-grown microkernel that runs on the line cards. My job
    responsibilities include developing and maintaining a platform development
    kit, keeping the core JUNOS clean to ensure portability to multiple
    platforms on multiple architectures.}

    \resitem{Tools for performance and scaling}{As part of the scaling effort
    in JUNOS kernel, I developed tools and build infrastructure to keep check
    on memory utilization and performance in scaled setups.}

    \resitem{In-service Software Upgrade}{I was part of the team that developed
    the infrastructure to support In-service software upgrade of single chassis
    Juniper routers. This enabled Juniper customers to upgrade their routers
    with minimal disruption in terms of traffic and no disruptions in the
    control plane. My contributions to the project were restricted to control
    plane, and included the main ISSU control flow, message versioning and the
    user interface. Later, I led a team of developers to extend the ISSU
    functionality to a multi-chassis router.}

    \resitem{JUNOS School, Best Practices etc}{I made significant contributions
    to JUNOS School - an initiative to ramp up new hires into JUNOS, and have
    done several technical presentations for audiences internal to Juniper. I
    have contributed to Juniper internal tools for code review, data collection
    from routers after crash and set of automated scripts to manage power
    consumption of lab routers when not in use.}

    \end{itemize}

  \ressubheading{Hewlett Packard}{Senior Software Engineer}{Jun 2003 - Oct 2004}
    \begin{itemize}

    \resitem{Drivers for Compaq hardware RAID cards}{Sustenance of Linux
    drivers for HP RAID cards - cpqarray and cpqfc. I was responsible for
    making bug-fix releases of driver binaries in RPM format for multiple
    versions of Linux distributions including Redhat Enterprise Linux, Fedora
    Linux and SuSE Linux Enterprise Server for multiple architectures (i386,
    amd64).}

    \resitem{BL10e rack of servers firmware}{Sustenance of Linux based firmware
    for chassis for BL10e blade servers. The chassis keeps track of the blades
    inserted and in-operation, monitors temperatures, controls fan speeds, and
    provides power management interface to the blades.}

    \resitem{OpenSSI}{Contributor to open source, Linux based cluster project
    called \href{http://www.openssi.org}{OpenSSI}. I developed several modules
    including multicast tftp based cluster bootup, and a process monitor. I was
    the release manager for the project, and made a few releases. I fixed
    non-compliance issues reported by Linux Test Project testsuite. I also
    worked with beta customers to help modify their software to scale better on
    the cluster.}

    \end{itemize}

  \ressubheading{Timesys, Inc.}{Senior Software Engineer}{Mar 2002 - Apr 2003}
    \begin{itemize}

    \resitem{Timesys Linux}{I was responsible for porting Timesys Linux to
    several PowerPC and StrongARM based single board computers from Embedded
    Planet, IBM, and Applied Data. I ported various open source applications,
    including Apache web server, windowing toolkit called picogui to PowerPC
    and StrongARM.}

    \end{itemize}

  \ressubheading{Epigon Audiocare Pvt Ltd}{Software Engineer}{Dec 1999 - Feb 2002}
    \begin{itemize}

    \resitem{C-sound driver}{I designed and implemented device driver,
    supporting libraries, userspace application for an in-house developed PCI
    card used to synthesis music using C-sound music descriptor language.}

    \resitem{Cleanroom implementation of JVM}{I developed a clean-room
    implementation of Java Virtual Machine conforming to subset of J2ME
    specification for Linux based embedded system which was later ported to
    Windows.}

    \end{itemize}
\end{itemize}

%-------------------------------------------------------------------------------
%-- Open Source  ---------------------------------------------------------------
%-------------------------------------------------------------------------------

%%% \vspace{0.1in}
%%% \resheading{Open Source}
%%% \vspace{0.1in}
%%% 
%%% I have been associated with a few open source projects, some professionally,
%%% and some as a hobby.
%%% 
%%% \begin{itemize}
%%%   \ressubheading{\href{http://waba.sourceforge.net}{Waba}}{JVM Implementation}{2000 - 2001}
%%%     \begin{itemize}
%%%     \item{Waba is a small, efficient and reliable Java Virtual Machine aimed at
%%%     portable devices. I contributed code to the class loader which loaded class
%%%     files from a .jar archive, and few other minor improvements in the
%%%     interpreter.}
%%%     \end{itemize}
%%% 
%%%   \ressubheading{\href{http://openssi.org}{OpenSSI}}{Linux cluster project}{2003 - 2004}
%%%     \begin{itemize}
%%%     \item{OpenSSI is Linux Cluster project sponsored by Hewlett Packard. I
%%%     worked on it when I was working for Hewlett Packard, as part of my regular
%%%     job. I worked on few features such as enabling parallel boot in a cluster
%%%     using multicast TFTP, replacing plain TFTP mechanism, and a process
%%%     monitor, which monitored a process over several nodes of the cluster. I
%%%     also fixed several bugs uncovered using LTP (Linux Test Project). I also
%%%     played the role of the release manager for a few releases. I also worked
%%%     with a couple of ISVs to help improve their software performance using
%%%     OpenSSI.}
%%%     \end{itemize}
%%% 
%%%   \ressubheading{\href{http://finplan.googlecode.com}{finplan}}{Finance planner}{2010}
%%%     \begin{itemize}
%%%     \item{This tool was written to help one plan his or her finances over a
%%%     period of time on the basis of the user inputs of periodic and one-time
%%%     expenses. The tool can generate histograms which can be displayed using
%%%     GNUplot.}
%%%     \end{itemize}
%%% 
%%%   \ressubheading{\href{http://gypsybsd.googlecode.com}{GypsyBSD}}{FreeBSD LiveCD}{2010}
%%%     \begin{itemize}
%%%     \item{The FreeBSD based LiveCD is designed to have minimal set of tools to
%%%     help me get onto the local network, and connect to servers where I can
%%%     continue with my work. I started writing this when I was provided a Windows
%%%     desktop when I was visiting the US office of my company.}
%%%     \end{itemize}
%%% 
%%%   \ressubheading{\href{http://bugster.googlecode.com}{Bugster}}{MP3 Sharing Software}{2001}
%%%     \begin{itemize}
%%%     \item{I had written this software to help me and my friends share MP3s over
%%%     a shared network.}
%%%     \end{itemize}
%%% \end{itemize}

%-------------------------------------------------------------------------------
%-- Education ------------------------------------------------------------------
%-------------------------------------------------------------------------------
\vspace{0.1in}
\resheading{Education}
  \begin{itemize}
  \ressubheading{Indian Institute of Technology, Bombay}
  {Mumbai, India}{Bachelor of Technology in Computer Science \& Engineering}
  {1995 - 2000}
  \end{itemize}

%-------------------------------------------------------------------------------
%-- Personal  ------------------------------------------------------------------
%-------------------------------------------------------------------------------
\vspace{0.1in}
\resheading{Personal}
  \begin{tabular*}{0.50\textwidth}{@{\hspace{2em}{\extracolsep{\fill}}} ll }
                  	&  			\\
    Date of Birth 	& December 1, 1976 	\\
    Nationality 	& Indian 		\\
    Marital Status 	& Married 		\\
  \end{tabular*}

%-------------------------------------------------------------------------------
% -- Footer --------------------------------------------------------------------
%-------------------------------------------------------------------------------

\vspace{0.5in}
\rule{\linewidth}{0.5mm}
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}

%-------------------------------------------------------------------------------
% -- EOF -----------------------------------------------------------------------
%-------------------------------------------------------------------------------
